The unequal distribution of access to education and transport: insights from

### 2016-06-06 paper.Rmd
Paper update from Ana
Comment out non-local data

```{r table-placeholder, echo=FALSE, warning=FALSE}
tbl = read.csv("public.csv")
names(tbl) = c("Mode", "Percent", "Duration (min)")
knitr::kable(tbl, row.names = T, caption = "Modal split by type of secondary school")
```

@@

```{r, echo=FALSE, fig.cap="Cumulative opportunity index", out.width="70%"}
knitr::include_graphics(c("cum_index.png"))
```

@@

```{r, echo=FALSE, fig.cap="Competitive accessibility index", out.width="70%"}
knitr::include_graphics(c("comp_index.png"))
```

>>>>

```{r table-placeholder, echo=FALSE, warning=FALSE}
# tbl = read.csv("public.csv")
# names(tbl) = c("Mode", "Percent", "Duration (min)")
# knitr::kable(tbl, row.names = T, caption = "Modal split by type of secondary school")
```

@@

```{r, echo=FALSE, fig.cap="Cumulative opportunity index", out.width="70%"}
# knitr::include_graphics(c("cum_index.png"))
```

@@

```{r, echo=FALSE, fig.cap="Competitive accessibility index", out.width="70%"}
# knitr::include_graphics(c("comp_index.png"))
```
